Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2022-02-08 metanalysis_visualization/manuscript_Figures.Rmd
integration of table 1

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
   mental_codes_qc_output <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all, mental_codes_qc_output)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, mental_codes_qc_output)
}
```

@@

```{r}
sitesWithTable1 <- outputFiles[c(1,3:5)]

for( i in 1:length( sitesWithTable1 )){
  print(i)
  load(paste0( outputDir, sitesWithTable1[i]))
  if( i == 1 ){
    table1_all <- table1
  } else {
    table1_all <- rbind( table1_all, table1)
  }
  rm( table1)
}
```

>>>>

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
   mental_codes_qc_output <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all, mental_codes_qc_output)
    table1_all <- rbind( table1_all, table1)
    }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, mental_codes_qc_output, table1)
}
```

@@

```{r}
sex_table1_all <- table1_all %>%
  filter( Category == "Sex" & name != "Total") %>%
  mutate( before_counts = sapply(strsplit( before_pandemic, " "), '[', 1), 
          during_counts = sapply(strsplit( during_pandemic, " "), '[', 1)) %>%
  group_by( name ) %>%
  summarise( before_pandemic_count = sum( as.numeric( before_counts )), 
             during_pandemic_count = sum( as.numeric( during_counts ))) %>%
  mutate( Category = "Sex") %>%
  select( Category, name, before_pandemic_count, during_pandemic_count )

sex_table1_all <- rbind( sex_table1_all, c("Total", "",sum( sex_table1_all$before_pandemic_count), sum( sex_table1_all$during_pandemic_count)))

dg_table1_all <- table1_all %>%
  filter( Category == "Disorder groups" & name != "Total") %>%
  mutate( before_counts = sapply(strsplit( before_pandemic, " "), '[', 1), 
          during_counts = sapply(strsplit( during_pandemic, " "), '[', 1)) %>%
  group_by( name ) %>%
  summarise( before_pandemic_count = sum( as.numeric( before_counts ), na.rm = TRUE), 
             during_pandemic_count = sum( as.numeric( during_counts ), na.rm = TRUE)) %>%
  mutate( Category = "Disorder groups") %>%
  select( Category, name, before_pandemic_count, during_pandemic_count )

table1 <- rbind( sex_table1_all, dg_table1_all )

table1 %>%
  kable( booktabs = T) %>%
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::group_rows(index = setNames(rle(table1$Category)[[1]], rle(table1$Category)[[2]]))
```

### 2022-02-08 psy_peds_3_CHOP.Rmd
integration of table 1

```{r}
table1 <- read.csv(file = "../output/CHOP/Table 1.csv")
table1 %>% 
   kable( booktabs = T) %>%
  kableExtra::kable_styling(latex_options = "striped") 
```

>>>>

```{r}
table1 <- read.csv(file = "../output/CHOP/Table 1.csv")

sex <- table1[ c(2:4), ] %>%
  mutate( Category = "Sex", 
          name = c("female", "male", "Total"),           
          before_pandemic = paste0( Before.Pandemic, " (", Before.Pandemic.1, " %)"), 
          during_pandemic = paste0( During.Pandemic, " (", During.Pandemic.1, " %)"), 
          pvalue = NA) %>%
  select( Category, name, before_pandemic, during_pandemic, pvalue)

age <- table1[ c(6), ] %>%
  mutate( Category = "Age", 
          name = "Age", 
          before_pandemic = paste0( Before.Pandemic, " (sd: ", Before.Pandemic.1, ")"), 
          during_pandemic = paste0( During.Pandemic, " (sd: ", During.Pandemic.1, ")"), 
          pvalue = NA
          ) %>%
  select( Category, name, before_pandemic, during_pandemic, pvalue)

t.test2 <- function(m1, m2, s1, s2, n1, n2) {
  # t.test computed from sample statistics, ie using mean, standard deviation and count value of the samples
  # useful in case we can only retrieve aggregated stats from the sites
  # ref: https://stats.stackexchange.com/questions/30394/how-to-perform-two-sample-t-tests-in-r-by-inputting-sample-statistics-rather-tha
  # and https://en.wikipedia.org/wiki/Student%27s_t-test?oldformat=true#Equal_or_unequal_sample_sizes,_unequal_variances_(sX1_%3E_2sX2_or_sX2_%3E_2sX1)
  se <- sqrt( (s1^2/n1) + (s2^2/n2) )
  # welch-satterthwaite df
  df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
  t <- (m1-m2)/se
  dat <- c(m1-m2, se, t, 2*pt(-abs(t),df))
  names(dat) <- c("Difference of means", "Std Error", "t", "p-value")
  return(dat)
}

age$pvalue <- t.test2(m1 = 14.51,
                    m2 = 14.56,
                    s1 = 1.89,
                    s2 = 1.84,
                    n1 = 2592,
                    n2 = 2419) %>%
  `[[`("p-value")

disorder_groups_t1 <- table1[ c(8:24), ] %>%
  mutate( Category = "Disorder groups", 
          name = X,           
          before_pandemic = paste0( Before.Pandemic, " (", Before.Pandemic.1, " %)"), 
          during_pandemic = paste0( During.Pandemic, " (", During.Pandemic.1, " %)"), 
          pvalue = NA
          ) %>%
  select( Category, name, before_pandemic, during_pandemic, pvalue)

table1 <- rbind( sex, age, disorder_groups_t1 )

table1 %>% 
  kable( booktabs = T) %>%
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::group_rows(index = setNames(rle(table1$Category)[[1]], rle(table1$Category)[[2]]))
```
